\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-16 paper.qmd
Updated the paper with new data structure

```{r}
#| label: two-curvy-training
training_data_two_curvy <- read_rds("data/two_curvy_diff_clust/two_curvy_diff_clust_data.rds")
```

@@

true_model_df <- read_rds("data/two_curvy_diff_clust/two_curvy_diff_clust_true_model.rds")
wireframe_true_model <- read_rds("data/two_curvy_diff_clust/two_curvy_diff_clust_true_model_connections.rds")

@@

<!--UMAP applied for Two curvy data-->
```{r}
#| label: umap-two-curvy
umap_two_curvy <- read_rds(file = "data/two_curvy_diff_clust/two_curvy_diff_clust_umap_n-neigbors_15_min-dist_0.1.rds")

@@

error_two_curvy_diff_clust_umap <- read_rds("data/two_curvy_diff_clust/error_two_curvy_diff_clust_umap.rds")

## Find the minimum MSE when have duplicate a1
error_two_curvy_diff_clust_umap <- error_two_curvy_diff_clust_umap |>
  group_by(a1) |>
  filter(bin1 == min(bin1)) |>
  ungroup() |>
  mutate(prop_dens = 1/(b*side_length^2))

base_line_prop_dens <- error_two_curvy_diff_clust_umap |>
  filter(a1 == min(a1)) |>
  pull(prop_dens)

error_two_curvy_diff_clust_umap <- error_two_curvy_diff_clust_umap |>
  mutate(prop_comp = prop_dens/base_line_prop_dens)

mse_two_curvy_b <- ggplot(error_two_curvy_diff_clust_umap, 
                     aes(x = a1, 
                         y = MSE)) +
  geom_vline(xintercept = 0.09,
             linetype="solid",
           color = "#d95f02", linewidth=1) +
  geom_vline(xintercept = 0.05,
             color = "#1b9e77", linetype=2,
             linewidth=1) +
  geom_vline(xintercept = 0.13, linetype=2,
             color = "#1f78b4", linewidth=1) +
  geom_line(linewidth = 0.5) + 
  geom_point(size = 1) +
  scale_x_continuous(breaks = sort(unique(round(error_two_curvy_diff_clust_umap$a1, 2)))[c(1, 4, 8, 10, 11, 12, 13, 14)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = "MSE") +
  ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

prop_dens_a1 <- ggplot(error_two_curvy_diff_clust_umap,
                     aes(x = a1,
                         y = prop_comp)) +
  geom_vline(xintercept = 0.09,
             linetype="solid",
           color = "#d95f02", linewidth=1) +
  geom_vline(xintercept = 0.05,
             color = "#1b9e77", linetype=2,
             linewidth=1) +
  geom_vline(xintercept = 0.13, linetype=2,
             color = "#1f78b4", linewidth=1) +
  geom_line(linewidth = 0.5) +
  geom_point(size = 1) +
  # scale_y_continuous(breaks = sort(unique(error_two_curvy$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_two_curvy_diff_clust_umap$a1, 2)))[c(1, 4, 8, 10, 11, 12, 13, 14)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = paste("Relative proportion density")) +
  ggtitle("(d)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

error_two_curvy_diff_clust_umap <- error_two_curvy_diff_clust_umap |>
  mutate(prop_bins = b_non_empty/b)

a1_m_two_curvy <- ggplot(error_two_curvy_diff_clust_umap,
                     aes(x = a1,
                         y = prop_bins)) +
  geom_vline(xintercept = 0.09,
             linetype="solid",
           color = "#d95f02", linewidth=1) +
  geom_vline(xintercept = 0.05,
             color = "#1b9e77", linetype=2,
             linewidth=1) +
  geom_vline(xintercept = 0.13, linetype=2,
             color = "#1f78b4", linewidth=1) +
  geom_line(linewidth = 0.5) +
  geom_point(size = 1) +
  # scale_y_continuous(breaks = sort(unique(error_two_curvy$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_two_curvy_diff_clust_umap$a1, 2)))[c(1, 4, 8, 10, 11, 12, 13, 14)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = expression(paste("proportion of non-empty bins ", bgroup("(", frac(m, b), ")")))) +
  ggtitle("(b)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

predict_umap_two_curvy <- read_rds(file = "data/two_curvy_diff_clust/two_curvy_diff_clust_umap_predict_true.rds")

@@

error_rm_two_curvy <- read_rds("data/two_curvy_diff_clust/error_rm_lwd_diff_bin.rds") |>
  mutate(bin1  = as.factor(bin1))

@@

```{r}
#| label: read-two-curvy-clust-nldr
# Read a variety of different NLDR representations of two_curvy_diff_clust
# and plot them on same aspect ratio
tsne_two_curvy_diff_clust <- read_rds("data/two_curvy_diff_clust/two_curvy_diff_clust_tsne_perplexity_30.rds")

nldr_two_curvy_diff_clust1 <- tsne_two_curvy_diff_clust |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("a", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

umap_two_curvy_diff_clust <- read_rds("data/two_curvy_diff_clust/two_curvy_diff_clust_umap_n-neigbors_15_min-dist_0.1.rds")

nldr_two_curvy_diff_clust2 <- umap_two_curvy_diff_clust |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour='#636363') +
  interior_annotation("b", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

phate_two_curvy_diff_clust <- read_rds("data/two_curvy_diff_clust/two_curvy_diff_clust_phate_knn_5.rds")

nldr_two_curvy_diff_clust3 <- phate_two_curvy_diff_clust |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  interior_annotation("c") +
  theme(aspect.ratio = 1)

trimap_two_curvy_diff_clust <- read_rds("data/two_curvy_diff_clust/two_curvy_diff_clust_trimap_n-inliers_12_n-outliers_4_n-random_3.rds")

nldr_two_curvy_diff_clust4 <- trimap_two_curvy_diff_clust |>
  ggplot(aes(x = TriMAP1,
             y = TriMAP2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  interior_annotation("d") +
  theme(aspect.ratio = 1)

pacmap_two_curvy_diff_clust <- read_rds("data/two_curvy_diff_clust/two_curvy_diff_clust_pacmap_n-neighbors_10_init_random_MN-ratio_0.5_FP-ratio_2.rds")

nldr_two_curvy_diff_clust5 <- pacmap_two_curvy_diff_clust |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("e") +
  theme(aspect.ratio = 1)
```

```{r}
#| label: combine-data-two_curvy_diff_clust

error_two_curvy_diff_clust_umap <- read_rds("data/two_curvy_diff_clust/error_two_curvy_diff_clust_umap.rds")
error_two_curvy_diff_clust_tsne <- read_rds("data/two_curvy_diff_clust/error_two_curvy_diff_clust_tsne.rds")
error_two_curvy_diff_clust_phate <- read_rds("data/two_curvy_diff_clust/error_two_curvy_diff_clust_phate.rds")
error_two_curvy_diff_clust_trimap <- read_rds("data/two_curvy_diff_clust/error_two_curvy_diff_clust_trimap.rds")
error_two_curvy_diff_clust_pacmap <- read_rds("data/two_curvy_diff_clust/error_two_curvy_diff_clust_pacmap.rds")

error_two_curvy_diff_clust <- bind_rows(error_two_curvy_diff_clust_umap, 
                         error_two_curvy_diff_clust_tsne,
                         error_two_curvy_diff_clust_phate,
                         error_two_curvy_diff_clust_trimap,
                         error_two_curvy_diff_clust_pacmap)

error_two_curvy_diff_clust <- error_two_curvy_diff_clust |>
  mutate(a1 = round(a1, 2)) |>
  filter(bin1 >= 5) |>
  group_by(method, a1) |>
  filter(MSE == min(MSE)) |>
  ungroup()
```

```{r}
#| label: error-comp-two_curvy_diff_clust

error_plot_two_curvy_diff_clust <- ggplot(error_two_curvy_diff_clust, 
                           aes(x = a1, 
                               y = MSE, 
                               colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_two_curvy_diff_clust$a1))[seq(1, length(unique(error_two_curvy_diff_clust$a1)), by = 5)]) +
  scale_color_manual(values=c('#e41a1c','#ff7f00','#4daf4a', "#a65628",'#636363')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

```{r}
#| fig-cap: "Assessing which of the 5 NLDR layouts on the two C-shaped clusters data is the better representation using MSE for varying binwidth ($a_1$). Colour used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-e). Layout d is universally poor. Layouts a that show two close clusters are universally suboptimal. Layout a is the best choice."
#| label: fig-two_curvy_diff_clust-mse
#| fig-pos: H
#| out-height: 60%

free(error_plot_two_curvy_diff_clust) + wrap_plots(nldr_two_curvy_diff_clust1, nldr_two_curvy_diff_clust2, nldr_two_curvy_diff_clust3, 
                                    nldr_two_curvy_diff_clust4, nldr_two_curvy_diff_clust5, ncol = 2)
```

@@

two_curvy_tsne_scaled_obj <- gen_scaled_data(
  data = tsne_two_curvy_diff_clust)

@@

tsne_two_curvy_diff_clust_plt <- tsne_two_curvy_scaled |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("b1", sc_ltr_pos) +
  theme(aspect.ratio = 1)

@@

nldr_two_curvy_original2 + tsne_two_curvy_diff_clust_plt +
  trimesh_two_curvy_removed1_with_data + trimesh_two_curvy_removed1_tsne_with_data +
  two_curvy_proj_umap_model2 +
  two_curvy_proj_tsne_model +
  two_curvy_proj_umap_all_model +
  two_curvy_proj_tsne_all_model +
  plot_layout(ncol = 2)
```

>>>>

```{r}
#| label: two-curvy-training
training_data_two_curvy <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_data.rds")
```

@@

true_model_df <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_true_model.rds")
wireframe_true_model <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_true_model_connections.rds")

@@

<!--UMAP applied for Two curvy data-->
```{r}
#| label: umap-two-curvy
umap_two_curvy <- read_rds(file = "data/two_c_shaped_clust/two_c_shaped_clust_umap_n-neigbors_15_min-dist_0.1.rds")

@@

error_two_c_shaped_clust_umap <- read_rds("data/two_c_shaped_clust/error_two_c_shaped_clust_umap.rds")

## Find the minimum MSE when have duplicate a1
error_two_c_shaped_clust_umap <- error_two_c_shaped_clust_umap |>
  group_by(a1) |>
  filter(bin1 == min(bin1)) |>
  ungroup() |>
  mutate(prop_dens = 1/(b*side_length^2))

base_line_prop_dens <- error_two_c_shaped_clust_umap |>
  filter(a1 == min(a1)) |>
  pull(prop_dens)

error_two_c_shaped_clust_umap <- error_two_c_shaped_clust_umap |>
  mutate(prop_comp = prop_dens/base_line_prop_dens)

mse_two_curvy_b <- ggplot(error_two_c_shaped_clust_umap, 
                     aes(x = a1, 
                         y = MSE)) +
  geom_vline(xintercept = 0.09,
             linetype="solid",
           color = "#d95f02", linewidth=1) +
  geom_vline(xintercept = 0.05,
             color = "#1b9e77", linetype=2,
             linewidth=1) +
  geom_vline(xintercept = 0.13, linetype=2,
             color = "#1f78b4", linewidth=1) +
  geom_line(linewidth = 0.5) + 
  geom_point(size = 1) +
  scale_x_continuous(breaks = sort(unique(round(error_two_c_shaped_clust_umap$a1, 2)))[c(1, 4, 8, 10, 11, 12, 13, 14)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = "MSE") +
  ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

prop_dens_a1 <- ggplot(error_two_c_shaped_clust_umap,
                     aes(x = a1,
                         y = prop_comp)) +
  geom_vline(xintercept = 0.09,
             linetype="solid",
           color = "#d95f02", linewidth=1) +
  geom_vline(xintercept = 0.05,
             color = "#1b9e77", linetype=2,
             linewidth=1) +
  geom_vline(xintercept = 0.13, linetype=2,
             color = "#1f78b4", linewidth=1) +
  geom_line(linewidth = 0.5) +
  geom_point(size = 1) +
  # scale_y_continuous(breaks = sort(unique(error_two_curvy$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_two_c_shaped_clust_umap$a1, 2)))[c(1, 4, 8, 10, 11, 12, 13, 14)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = paste("Relative proportion density")) +
  ggtitle("(d)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

error_two_c_shaped_clust_umap <- error_two_c_shaped_clust_umap |>
  mutate(prop_bins = b_non_empty/b)

a1_m_two_curvy <- ggplot(error_two_c_shaped_clust_umap,
                     aes(x = a1,
                         y = prop_bins)) +
  geom_vline(xintercept = 0.09,
             linetype="solid",
           color = "#d95f02", linewidth=1) +
  geom_vline(xintercept = 0.05,
             color = "#1b9e77", linetype=2,
             linewidth=1) +
  geom_vline(xintercept = 0.13, linetype=2,
             color = "#1f78b4", linewidth=1) +
  geom_line(linewidth = 0.5) +
  geom_point(size = 1) +
  # scale_y_continuous(breaks = sort(unique(error_two_curvy$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_two_c_shaped_clust_umap$a1, 2)))[c(1, 4, 8, 10, 11, 12, 13, 14)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = expression(paste("proportion of non-empty bins ", bgroup("(", frac(m, b), ")")))) +
  ggtitle("(b)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

predict_umap_two_curvy <- read_rds(file = "data/two_c_shaped_clust/two_c_shaped_clust_umap_predict_true.rds")

@@

error_rm_two_curvy <- read_rds("data/two_c_shaped_clust/error_rm_lwd_diff_bin.rds") |>
  mutate(bin1  = as.factor(bin1))

@@

```{r}
#| label: read-two-curvy-clust-nldr
# Read a variety of different NLDR representations of two_c_shaped_clust
# and plot them on same aspect ratio
tsne_two_c_shaped_clust <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_tsne_perplexity_30.rds")

nldr_two_c_shaped_clust1 <- tsne_two_c_shaped_clust |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("a", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

umap_two_c_shaped_clust <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_umap_n-neigbors_15_min-dist_0.1.rds")

nldr_two_c_shaped_clust2 <- umap_two_c_shaped_clust |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour='#636363') +
  interior_annotation("b", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

phate_two_c_shaped_clust <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_phate_knn_5.rds")

nldr_two_c_shaped_clust3 <- phate_two_c_shaped_clust |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  interior_annotation("c") +
  theme(aspect.ratio = 1)

trimap_two_c_shaped_clust <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_trimap_n-inliers_12_n-outliers_4_n-random_3.rds")

nldr_two_c_shaped_clust4 <- trimap_two_c_shaped_clust |>
  ggplot(aes(x = TriMAP1,
             y = TriMAP2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  interior_annotation("d") +
  theme(aspect.ratio = 1)

pacmap_two_c_shaped_clust <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_pacmap_n-neighbors_10_init_random_MN-ratio_0.5_FP-ratio_2.rds")

nldr_two_c_shaped_clust5 <- pacmap_two_c_shaped_clust |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("e") +
  theme(aspect.ratio = 1)
```

```{r}
#| label: combine-data-two_c_shaped_clust

error_two_c_shaped_clust_umap <- read_rds("data/two_c_shaped_clust/error_two_c_shaped_clust_umap.rds")
error_two_c_shaped_clust_tsne <- read_rds("data/two_c_shaped_clust/error_two_c_shaped_clust_tsne.rds")
error_two_c_shaped_clust_phate <- read_rds("data/two_c_shaped_clust/error_two_c_shaped_clust_phate.rds")
error_two_c_shaped_clust_trimap <- read_rds("data/two_c_shaped_clust/error_two_c_shaped_clust_trimap.rds")
error_two_c_shaped_clust_pacmap <- read_rds("data/two_c_shaped_clust/error_two_c_shaped_clust_pacmap.rds")

error_two_c_shaped_clust <- bind_rows(error_two_c_shaped_clust_umap, 
                         error_two_c_shaped_clust_tsne,
                         error_two_c_shaped_clust_phate,
                         error_two_c_shaped_clust_trimap,
                         error_two_c_shaped_clust_pacmap)

error_two_c_shaped_clust <- error_two_c_shaped_clust |>
  mutate(a1 = round(a1, 2)) |>
  filter(bin1 >= 5) |>
  group_by(method, a1) |>
  filter(MSE == min(MSE)) |>
  ungroup()
```

```{r}
#| label: error-comp-two_c_shaped_clust

error_plot_two_c_shaped_clust <- ggplot(error_two_c_shaped_clust, 
                           aes(x = a1, 
                               y = MSE, 
                               colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_two_c_shaped_clust$a1))[seq(1, length(unique(error_two_c_shaped_clust$a1)), by = 5)]) +
  scale_color_manual(values=c('#e41a1c','#ff7f00','#4daf4a', "#a65628",'#636363')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

```{r}
#| fig-cap: "Assessing which of the 5 NLDR layouts on the two C-shaped clusters data is the better representation using MSE for varying binwidth ($a_1$). Colour used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-e). Layout d is universally poor. Layouts a that show two close clusters are universally suboptimal. Layout a is the best choice."
#| label: fig-two_c_shaped_clust-mse
#| fig-pos: H
#| out-height: 60%

free(error_plot_two_c_shaped_clust) + wrap_plots(nldr_two_c_shaped_clust1, nldr_two_c_shaped_clust2, nldr_two_c_shaped_clust3, 
                                    nldr_two_c_shaped_clust4, nldr_two_c_shaped_clust5, ncol = 2)
```

@@

two_curvy_tsne_scaled_obj <- gen_scaled_data(
  data = tsne_two_c_shaped_clust)

@@

tsne_two_c_shaped_clust_plt <- tsne_two_curvy_scaled |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("b1", sc_ltr_pos) +
  theme(aspect.ratio = 1)

@@

nldr_two_curvy_original2 + tsne_two_c_shaped_clust_plt +
  trimesh_two_curvy_removed1_with_data + trimesh_two_curvy_removed1_tsne_with_data +
  two_curvy_proj_umap_model2 +
  two_curvy_proj_tsne_model +
  two_curvy_proj_umap_all_model +
  two_curvy_proj_tsne_all_model +
  plot_layout(ncol = 2)
```

### 2024-10-16 paper.tex
Updated Figure 9
Updated the paper with new data structure

\caption{\label{fig-param-two-curvy}Various plots to help assess best
hexagon bin parameters and thresholds to remove low-density bins. Both
(a) and (c) show MSE, against binwidth (\(a_1\)) and threshold. A good
benchmark value for these parameters is when the MSE drops and then
flattens out. Three binwidth choices were made: \(0.05\), \(0.09\), and
\(0.12\) to investigate. As the binwidth increases, the proportion of
non-empty bins also increases. There are two peaks at binwidths \(0.09\)
and \(0.12\). The relative proportion density decreases and levels off.
Binwidths \(0.05\) is the favorable choices. Based on the MSE, \(0.09\)
was chosen as the initial best binwidth for further analysis. There is
no need to remove the low-density hexagons because as shown in (b),
there is no considerable drop in MSE.}

@@

\includegraphics[width=1\textwidth,height=0.6\textheight]{paper_files/figure-pdf/fig-two_curvy_diff_clust-mse-1.pdf}

@@

\caption{\label{fig-two_curvy_diff_clust-mse}Assessing which of the 5
NLDR layouts on the two C-shaped clusters data is the better
representation using MSE for varying binwidth (\(a_1\)). Colour used for
the lines and points in the left plot and in the scatterplots represents
NLDR layout (a-e). Layout d is universally poor. Layouts a that show two
close clusters are universally suboptimal. Layout a is the best choice.}

>>>>

\caption{\label{fig-param-two-curvy}Various plots to help assess best
hexagon bin parameters and thresholds to remove low-density bins. Both
(a) and (c) show MSE, against binwidth (\(a_1\)) and threshold. A good
benchmark value for these parameters is when the MSE drops and then
flattens out. Three binwidth choices were made: \(0.05\), \(0.09\), and
\(0.13\) to investigate. As the binwidth increases, the proportion of
non-empty bins also increases. There are two peaks at binwidths \(0.09\)
and \(0.13\). The relative proportion density decreases and levels off.
Binwidths \(0.05\) is the favorable choices. Based on the MSE, \(0.09\)
was chosen as the initial best binwidth for further analysis. There is
no need to remove the low-density hexagons because as shown in (b),
there is no considerable drop in MSE.}

@@

\includegraphics[width=1\textwidth,height=0.6\textheight]{paper_files/figure-pdf/fig-two_c_shaped_clust-mse-1.pdf}

@@

\caption{\label{fig-two_c_shaped_clust-mse}Assessing which of the 5 NLDR
layouts on the two C-shaped clusters data is the better representation
using MSE for varying binwidth (\(a_1\)). Colour used for the lines and
points in the left plot and in the scatterplots represents NLDR layout
(a-e). Layout d is universally poor. Layouts a that show two close
clusters are universally suboptimal. Layout a is the best choice.}
